{\bf Simulating a two dimensional particle in a square quantum box with CUDA}

### 2013-08-30 paper/paper.tex
Added the documentation and code for a Command line UI

    \subsection{GUI and Configuration}
    The GUI is simple; it consists of a window where the simulation is drawn on
    as described in ~\ref{sec:synopsis}. The user can control the simulation using keystrokes listed bellow.
    \begin{center}
        \begin{tabular}{|r|r|}
        \hline
            . & Increase the time offset (Animation runs faster) \\ \hline
            , & Decrease the time offset (Animation runs slower) \\ \hline
            SPACE & Toggle pausing \\ \hline
            0 & Reset the animation (t = 0) \\ \hline
            ESC & Quit the simulation \\ \hline
        \end{tabular}
    \end{center}
    As well, the user can control the number of wave functions that are being simulated using
    command line arguments as follow
    \begin{verbatim}pbox n\end{verbatim}
    Where \verb|n| is the number of wave functions the user wishes to simulate.

@@

    \vspace{1cm}
    \subsection{Global Variables}
    The program uses these global variables
    \begin{itemize}
        \item \verb|cudaGraphicsResource *resource|\\\mar- The graphics resource that is
              linked to the OpenGL environment.
        \item \verb|GLuint buffer|\\\mar- The buffer used by OpenGL.
        \item \verb|float INCREASE_TIME|\\\mar- The time offset used to increase the time
              between the frames.
        \item \verb|particle p|\\\mar- The particle that the program is about.
        \item \verb|float t|\\\mar- The current time (set as the offset).
        \item \verb|int frames|\\\mar- The number of frames.
        \item \verb|float total_time|\\\mar- The total time.
        \item \verb|int PAUSE|\\\mar- Whether the animation is paused.
    \end{itemize}

@@

>>>>

    \subsection{GUI, Command line UI and User Configuration}
    The GUI is simple; it consists of a window where the simulation is drawn on
    as described in ~\ref{sec:synopsis}. The user can control the simulation using keystrokes listed bellow.
    \begin{center}
        \begin{tabular}{|r|l|}
        \hline
            . & Increase the time offset (Animation runs faster) \\ \hline
            , & Decrease the time offset (Animation runs slower) \\ \hline
            n & Go back one frame \\ \hline
            m & Go forward one frame\\ \hline
            SPACE & Toggle pausing \\ \hline
            0 & Reset the animation (t = 0) \\ \hline
            ESC & Quit the simulation \\ \hline
        \end{tabular}
    \end{center}
    As well, the user can control the number of wave functions that are being simulated using
    command line arguments as follow
    \begin{verbatim}pbox n\end{verbatim}
    Where \verb|n| is the number of wave functions the user wishes to simulate.\\\\
    {\bf UDPATE} A command line UI is used to display in an ordered fashion the state of the simulation
    (time, energy levels, average time per frame and the increment used by the animation), as well it
    displays the probabilities for each wave function and keyboard shortcuts and how to use the application.\\
    The command line UI was built using the \verb|curses| library available on Linux, and in the latest
    release of Xcode but unavailable directly on Windows\footnote{PDCurses is an alternative suggested
    by many http://pdcurses.sourceforge.net/. The author did not test it!}.\\
    This is a screenshot of the command line UI.\\\\
    \begin{figure}[hb]
        \centering
        \includegraphics[width=14cm]{graphics/cmdui.png}
        \caption{Command-Line UI}
    \end{figure}

@@

    \vspace{1cm}
    \subsection{Global Variables}
    The program uses these global variables
    \begin{itemize}
        \item \verb|cudaGraphicsResource *resource|\\\mar- The graphics resource that is
              linked to the OpenGL environment.
        \item \verb|GLuint buffer|\\\mar- The buffer used by OpenGL.
        \item \verb|float INCREASE_TIME|\\\mar- The time offset used to increase the time
              between the frames.
        \item \verb|particle p|\\\mar- The particle that the program is about.
        \item \verb|float t|\\\mar- The current time (set as the offset).
        \item \verb|int frames|\\\mar- The number of frames.
        \item \verb|float total_time|\\\mar- The total time.
        \item \verb|int PAUSE|\\\mar- Whether the animation is paused.
        \item \verb|WINDOW* window|\\\mar- The window variable used by \verb|ncurses| library.
        \item \verb|int ncols, nrows|\\\mar- The number of cols and rows in the \verb|window| variable.
    \end{itemize}

@@

        \vspace{1cm}
        \subsubsection{void clear\_row(int y)}
        This function uses the \verb|ncuses| library to clear a row, i.e. to fill it with
        empty characters with the background attitude.\\
        \\{\bf Parameters}\\
        \verb|int y|\\\mar- The row number to clear.

        \vspace{1cm}
        \subsubsection{void cmd\_display()}
        This function creates and fills the Command line UI using the \verb|ncurses| library.

        \vspace{1cm}
        \subsubsection{void init\_curses()}
        This function initiates the \verb|curses| environment and fills the variables \verb|window|,
        \verb|nrows|, \verb|ncols|, creates the colors for the background and text messages.
